%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}
\usepackage[
  a4paper,
  left=0.50in,
  right=0.50in,
  top=0.55in,
  bottom=0.55in
]{geometry}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%----------HELVETICA FONT----------
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{2pt}]



% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\huge \scshape EMMANUEL P. BARRAMEDA} \\ \vspace{1pt}
    \scriptsize
    +63 929 416 2224 $|$ \href{mailto:emmanpbarrameda@gmail.com}{\underline{emmanpbarrameda@gmail.com}} $|$ 
    \href{https://emmanpbarrameda.github.io/}
    {Portfolio: \underline{emmanpbarrameda.github.io}} $|$
    \href{https://github.com/emmanpbarrameda}
    {GitHub: \underline{github.com/emmanpbarrameda}}
    \normalsize
\end{center}

%-----------Objective-----------
\section{Professional Summary}
{\small
\begin{justify}
\vspace{-2pt}
Full-stack Software Engineer with 5+ years of experience across freelance and corporate roles, building and deploying production-grade web applications, internal systems, and RESTful APIs. Promoted to Software Engineer within 6 months at Casterly Ventures Corp. for independently delivering three production systems. Specialized in Laravel and the TALL stack, with hands-on expertise in CI/CD pipelines, Linux VPS management, Redis, WebSockets, and database optimization. Author of open-source Composer packages with 8,300+ downloads. Self-driven and experienced working independently across remote and on-site environments.
\vspace{-4pt}
\end{justify}
}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {... Intern}{January 2025 -- April 2025}
    %   {Company Here}{Place Here}
    %   \resumeItemListStart
    %     \resumeItem{.....}
    %     \resumeItem{.....}
    %     \resumeItem{.....}
    %   \resumeItemListEnd

\resumeSubheading
  {Software Engineer}{January 2026 - Present}
  {\href{https://casterly.ph/}{Casterly Ventures Corp.}}{Pasig City, Philippines}
  \resumeItemListStart
    \resumeItem{Promoted within 6 months for leading delivery of three production systems.}
    \resumeItem{Migrated production to a self-managed Linux VPS Server (Ubuntu 24.04, Nginx, CloudPanel), cutting hosting costs by 72\% with 4x more RAM and 2x more CPU cores.}
    \resumeItem{Built atomic GitHub Actions CI/CD pipelines and managed Redis queue infrastructure (8 workers), reducing deploy time by 70\%.}
    \resumeItem{Developed a POS system with barcode scanning, cart management, and dynamic pricing, eliminating manual sales processing for the sales team.}
    \resumeItem{Built a Warehouse Management System integrated with the IMS, improving inventory traceability across warehouse operations.}
    \resumeItem{Optimized system performance via composite database indexes and Redis caching, and integrated Google Drive API for automated cloud backup of generated reports.}
  \resumeItemListEnd

\resumeSubheading
  {Software Developer}{July 2025 - December 2025}
  {\href{https://casterly.ph/}{Casterly Ventures Corp.}}{Pasig City, Philippines}
  \resumeItemListStart
    \resumeItem{Built casterly.ph full-stack with a custom Filament CMS, enabling non-technical staff to manage content without developer involvement.}
    \resumeItem{Configured domain management and Cloudflare DNS, SSL, and security rules for site and shop.}
    \resumeItem{Built the e-commerce back-end (shop.casterly.ph) with order processing, payment integration, promo codes, reviews, and real-time shipment tracking via TrackingMore API.}
    \resumeItem{Developed a full-stack IMS for ITAD operations processing 2,200+ devices through an automated 8-stage workflow, architected as a modular monolith with service-layer pattern and config-driven design to support long-term maintainability and scalability using Laravel and FilamentPHP.}
    \resumeItem{Implemented Blancco/Speccy XML parsing for automated laptop spec extraction and queued Excel/PDF reporting; integrated Laravel Reverb via WebSockets for real-time inventory and workflow updates.}
  \resumeItemListEnd
    

    \resumeSubheading
      {Backend Developer Intern}{February 2025 - April 2025}
      {\href{https://bapplware.com/}{Bapplware Technologies, Inc.}}{Mandaluyong City, Philippines}
        \resumeItemListStart
            \resumeItem{Developed RESTful API modules for the HRP-API platform using PHP Symfony in Agile workflows.}
            \resumeItem{Implemented error handling, soft deletes, and timestamps to improve API reliability and data integrity.}
          \resumeItem{Wrote PHPUnit test cases to ensure code quality and catch regressions before deployment.}
          \resumeItem{Contributed to Agile sprints remotely, including sprint planning, daily standups, and feature delivery.}
        \resumeItemListEnd

    \resumeSubheading
      {Freelance Developer}{June 2020 - January 2025}
      {Remote}{}
      \resumeItemListStart
        \resumeItem{Designed and delivered custom software systems for government and academic clients across 5+ years.}
        \resumeItem{Built a desktop Employee Management System for the Philippine Air Force Headquarters Service Support Group (HSSG) using Java Swing, with role-based access control and reporting.}
        \resumeItem{Developed a web-based Student Internship System for the University of Rizal System using Laravel and FilamentPHP, deployed for student use.}
      \resumeItemListEnd

    
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd



%-----------KEY PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/emmanpbarrameda/filament-take-picture-field}
      {\textbf{Filament Take Picture Field} $|$ \emph{PHP, Laravel, FilamentPHP, Composer Package}}}{Open Source Initiative}
      \resumeItemListStart
        \resumeItem{Created and maintained an open-source FilamentPHP form field plugin for capturing images directly from the browser camera, with \textbf{32 GitHub stars} and \textbf{8,300+ downloads}.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\href{https://github.com/emmanpbarrameda/laravel-scheduled-maintenance}
      {\textbf{Laravel Scheduled Maintenance} $|$ \emph{PHP, Laravel, Queue, Composer Package}}}{Open Source Initiative}
      \resumeItemListStart
        \resumeItem{Modernized and maintained an open-source Laravel package for scheduling maintenance windows, showing downtime notices, supporting bypass links, and queue-based maintenance bypass for Laravel 10, 11, and 12.}
      \resumeItemListEnd

    \resumeProjectHeading
        {\href{https://ursb-itsl.vercel.app/}
        {\textbf{URSB-ITSL Website} $|$ \emph{React, TypeScript, Vite}}}{Front-end Development}
        \resumeItemListStart
            \resumeItem{Built and deployed the official website for the URSB BSIT Students' League with static site optimization and SEO.}
        \resumeItemListEnd

    % \resumeProjectHeading
    %     {\href{https://emmanpbarrameda.github.io/dev-notes/}
    %     {\textbf{Dev Notes} $|$ \emph{Astro, Markdown, GitHub Pages}}}{Front-end Development}
    %     \resumeItemListStart
    %         \resumeItem{Maintain a technical blog on GitHub Pages, sharing development insights, solutions, and practical programming notes.}
    %     \resumeItemListEnd
      
    \resumeProjectHeading
      {\href{https://github.com/emmanpbarrameda/GIT-RAWify}
      {\textbf{GIT.RAWify} $|$ \emph{JavaScript, Bootstrap}}}{Front-end Development}
      \resumeItemListStart
        \resumeItem{Built a developer tool that converts GitHub links into raw content URLs, generating over \textbf{86K impressions} and \textbf{3.39K clicks}.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\href{https://mmchurch.online}
      {\textbf{MMC MIS (Capstone Project)} $|$ \emph{Laravel, FilamentPHP, MySQL, AI}}}{September 2023 - March 2025}
      \resumeItemListStart
        \resumeItem{Led the team as Project Manager and Lead Developer in building a church Management Information System that streamlined administrative workflows and won \textbf{Best Software Developmental Study} at the 18th Campus Research Congress.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\href{https://iotc-mis.site/}{\textbf{IOTC Seafarer Application System}} $|$ \emph{Laravel, FilamentPHP, Face Recognition}}{Client Capstone Project}
      \resumeItemListStart
        \resumeItem{Built a full-stack seafarer certification system for a freelance client, covering application submissions, exams, interviews, facial recognition attendance, and real-time status tracking using Laravel and FilamentPHP.}
      \resumeItemListEnd
      
    \resumeProjectHeading
          {\textbf{URSB Internship System} $|$ \emph{Laravel, FilamentPHP, MySQL}}{Client Capstone Project}
          \resumeItemListStart
            \resumeItem{Developed a web-based Internship Management System for the University of Rizal System, enabling students to manage internship requirements, progress, and personal records.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Primary Stack}{: PHP, Laravel, Livewire, Alpine.js, Tailwind CSS, Blade, MySQL, Redis, FilamentPHP} \\
     \textbf{Frontend}{: JavaScript, Vue.js, jQuery, HTML/CSS, Bootstrap, React.js, TypeScript, Vite} \\
     \textbf{DevOps \& Infrastructure}{: Linux (Ubuntu), Nginx, Cloudflare, Docker, CloudPanel, GitHub Actions, Git} \\
     \textbf{Tools}{: PHPUnit, Postman, Composer} \\
     \textbf{Other Languages}{: Java, C\#, VB.Net} \\
     \textbf{Methodologies}{: Agile (Scrum), Kanban} \\
    }}
\end{itemize}




%-----------EDUCATION & LEADERSHIP-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {University of Rizal System}{Binangonan, Rizal}
    {Bachelor of Science in Information Technology}{Aug 2022 -- Jun 2025}
    \resumeItemListStart
      % \resumeItem{Student Organization President, BSIT Students' League (2024--2025)}
      % \resumeItem{Student Organization Public Information Officer, URSB Graduating Class 2025}
      % \resumeItem{Member, URS Binangonan Electoral Tribunal (2024–2025)}
      % \resumeItem{Student Organization Vice President, BSIT Students' League (2023–2024)}
      \resumeItem{Student Organization President (2024-2025) and Vice President (2023–2024) of the URSB BSIT Students' League; Public Information Officer (PIO) of the URSB Graduating Class 2025.}
    \resumeItemListEnd

  % \resumeSubheading
  %   {East Systems Colleges of Rizal}{Morong, Rizal}
  %   {Bachelor of Science in Information Technology}{Oct 2020 -- Jun 2022 (Transferred-out to URS)}

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}